Relating games of Menger, countable fan tightness, and selective separability

### 2016-10-12 articles/relating-games-menger-cft-ss/article.tex
awful commit message, just see the diff

@@

\begin{proof}

\end{proof}

@@

\begin{proof}
  Since \(\mc D_X\subseteq \mc B_{X,x}\), the second condition trivially
  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
  are characterized by \(C(D)FT_{\vec 0}\). So the result follows from the
  previous lemmas.
\end{proof}

>>>>

\begin{proposition}
  Any witness for \(\Omega M\) (resp. \(\Omega M^+,\Omega M^{+mark}\))
  may be improved such that any final sequence of the chosen
  finite subcollections is an \(\omega\)-cover.
\end{proposition}

\begin{proof}
  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of open covers.
  For \(\Omega M\), choose the witness
  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) for the final
  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\) for each \(n<\omega\),
  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\).
  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
  \(\tau\) where
  \(
    \tau(\<\mc U_0,\dots,\mc U_n\>)
      =
    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
  \). For \(\Omega M^{+mark}\), the winning Markov strategy \(\sigma\) may
  be improved to \(\tau\) where
  \(
    \tau(\mc U,n)
      =
    \bigcup_{i\leq n}\sigma(\mc U,i)
  \).
\end{proof}

@@

\begin{proof}
  For each \(B\in\mc B_{C_p(X),\vec 0}\) define
  \[
    \mc U_n(B)
      =
    \left\{
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
    :
      \vec x\in B
    \right\}
  .\]
  Consider the finite set \(F\in[X]^{<\omega}\). Since
  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
  It follows that \(F\subseteq x^{-1}[(-1,1)]\in\mc U_n(B)\),
  so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).

  Consider the sequence of blades
  \(\<B_0,B_1,\dots\>\in\mc B_{C_p(X),\vec 0}^\omega\), and the
  corresponding sequence of \(\omega\)-covers
  \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).

  Assuming \(X\) is \(\Omega M\), choose a witness
  \(\<\mc F_0,\mc F_1,\dots\>\) such that
  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
  \[
    \bigcup_{i\leq n<\omega} \mc F_n
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    F_n
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \mc F_n
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}F_n\).

  Assuming \(X\) is \(\Omega M^+\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(\<B_0,\dots,B_n\>)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).

  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
  \(\sigma\) such that
  \[
    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
  \]
  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
  Now let
  \[
    \tau(B_n,n)
      =
    \left\{
      \vec x\in B_n
    :
      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
        \in
      \sigma(\mc U_n(B_n),n)
    \right\}
  .\]
  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
  \(\frac{1}{2^i}<\epsilon\) and then choose
  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
  every basic open neighborhood of \(\vec 0\) intersects
  \(\bigcup_{n<\omega}\tau(B_n,n)\).
\end{proof}

@@

\begin{proof}
  Since \(\mc D_X\subseteq \mc B_{X,x}\), the second condition trivially
  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
  follow from \(C(D)FT_{\vec 0}\). So the result follows from the
  previous lemmas.
\end{proof}

\section{A space which is \(CFT^+\) but not \(CDFT^{+mark}\)}

Our goal is to now demonstrate a space which is \(CFT^+\),
but not even \(CDFT^{+mark}\). To do so, we will find a space \(X\)
which is \(\Omega M^+\) but not \(\Omega M^{+mark}\), yielding \(C_p(X)\)
as our example.

\begin{proposition}\label{altCompactCharacterization}
  A space \(X\) is compact if and only if for each \(\omega\)-cover
  \(\mc U\) of \(X\) and \(n<\omega\), there exists a finite subcollection
  \(\mc F\in[\mc U]^{<\omega}\) such that for each \(F\in[X]^{\leq n}\)
  there exists some \(U\in\mc F\) where \(F\subseteq U\).
\end{proposition}

\begin{proof}
  Let \(X\) and therefore \(X^n\) be compact.
  Let \(\mc F_n\) be the finite subcover of the
  open cover \(\mc U_n=\{U^n:U\in\mc U\}\). Then
  \(\mc F=\{U:U^n\in\mc F_n\}\) witnesses our desired result.
\end{proof}

\begin{lemma}
  The following are equivalent for a regular topological space \(X\):
  \begin{itemize}
    \item \(X\) is \(\sigma\)-compact
    \item \(X\) is \(\Omega M^{+mark}\)
    \item \(X\) is \(M^{+mark}\)
  \end{itemize}
\end{lemma}

\begin{proof}
  The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
  was shown in \cite{clontzMengerGamePreprint}. As \(\Omega M^{+mark}\)
  trivially implies \(M^{+mark}\), we need only demonstrate that
  if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
  then \(X\) is \(\Omega M^{+mark}\).

  We define \(\sigma(\mc U,n)\) for each \(\omega\)-cover \(\mc U\) and
  \(n<\omega\) to witness Proposition \ref{altCompactCharacterization}
  for \(\mc U\), \(K_n\), and \(n\). It follows that for every sequence of
  \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\) and \(F\in[X]^{<\omega}\),
  \(F\in[K_n]^{\leq n}\) for some \(n\geq|F|\), and thus there exists some
  \(U\in\sigma(\mc U_n,n)\) where \(F\subseteq U\). Therefore
  \(\bigcup_{n<\omega}\sigma(\mc U,n)\) is an \(\omega\)-cover of \(X\).
\end{proof}

\begin{definition}
  Let \(X\) be a topological space such that all countable sets are
  closed. Then \(\onePtLind{X}=X\cup\{\infty\}\)
  is the \term{one-point Lindel\"of-ication} of \(X\), with a basis given
  by the usual open sets of \(X\) and the co-countable sets containing
  \(\infty\).
\end{definition}

\begin{theorem}
  Let \(\omega_1\) have the discrete topology. Then
  \(\onePtLind{\omega_1}\) is \(\Omega M^+\) but not \(\Omega M^{+mark}\).
\end{theorem}

\begin{proof}
  The proof that \(X=\onePtLind{\omega_1}\) is not
  \(\sigma\)-compact is simply the fact that its countably infinite subsets
  are closed and discrete.
  We define the strategy \(\sigma\) for \(\plII\) in
  \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.

  % Let \(\sigma_0(\<\mc U_0\>)=\{I_0\}\) where \(I_0\) is a co-countable set
  % containing \(\infty\). Denote
  % \(\onePtLind{\omega_1}\setminus I_0=\{\alpha_{0,n}:n<\omega\}\),
  % and then let \(\sigma_0(\<\mc U_0,\dots,\mc U_{n+1}\>)\) contain exactly
  % one superset of \(\{\infty\}\cup\{\alpha_{0,n}\}\).

  For \(n<\omega\)
  let \(\sigma_n(\<\mc U_n\>)=\{I_n\}\)
  where \(I_n\) is a co-countable set containing \(\infty\).
  Denote
  \(\onePtLind{\omega_1}\setminus I_n=\{\alpha_{n,m}:m<\omega\}\),
  and then for \(m<\omega\)
  let \(\sigma_n(\<\mc U_n,\dots,\mc U_{n+m}\>)\) contain exactly
  one set, a superset of \(\{\infty\}\cup\{\alpha_{i,j}:i\leq n,j\leq n+m\}\).

  TODO: finish
\end{proof}
